### 2018-03-26 tex/paper.tex
small mods.

\noindent
\sjtnote{This is a preliminary version, return to this at the end of the writing process.}

@@

In designing, Marlowe we have chosen a number of options; this description applies to Marlowe version 1.2 \sjtnote{Is 
there an obvious way of making that clear in the repo? I really don't understand how git deals with ``releases'' or 
versions.}\plsnote{We can create a branch and point to that.}

@@

While earlier versions used a ``push'' model of operations, we have revised the language to give a ``pull'' semantics. 
This means, for example, that the language can \emph{enable} a payment to be made, but cannot make the payment happen. 
It is up to the interested party (or parties) to make the change happen. It is therefore possible for the payment not to 
happen, despite the fact that this is against the interest of the receiving party.\plsnote{There was a trailing ``the 
same'' here. Did you think of another example?}

\paragraph{UTxO vs.\ accounts} \sjtnote{Pablo: please check this section carefully}

@@

Does the \haskellinline{Both} constructor potentially produce invalid/misleading contracts, combining a commitment in 
one half with its use in the other? The problem is that the ``use'' conjunct could potentially be executed, leading to 
a failed payment. \plsnote{What do you mean with the ``use'' conjunct?}

@@

\sjtnote{I have expanded this to include a number of responses to Charles' comments on an earlier document. Other responses appear in the previous sub-section.}

@@

\sjtnote{Have I forgotten anyone?}

Thanks to IOHK staff Manuel Chakravarty, Duncan Coutts, Bernardo David, Charles Hoskinson, Aggelos Kiyakis, Darryl 
McAdams, Bruno Woltzenlogel Paleo, and Phil Wadler for their collaboration, and to colleagues from the Universities of 
Kent and Leicester for their comments on previous presentations of this work.

>>>>

@@

In designing, Marlowe we have chosen a number of options; this description applies to Marlowe version 1.2

@@

While earlier versions used a ``push'' model of operations, we have revised the language to give a ``pull'' semantics. 
This means, for example, that the language can \emph{enable} a payment to be made, but cannot make the payment happen. 
It is up to the interested party (or parties) to make the change happen. It is therefore possible for the payment not to 
happen, despite the fact that this is against the interest of the receiving party.

\paragraph{UTxO vs.\ accounts}

@@

Does the \haskellinline{Both} constructor potentially produce invalid/misleading contracts, combining a commitment in 
one half with its use in the other? The problem is that this might potentially lead to 
a failed payment.

@@

@@

Thanks to IOHK staff Manuel Chakravarty, Duncan Coutts, Bernardo David, Charles Hoskinson, Aggelos Kiayias, Darryl 
McAdams, Bruno Woltzenlogel Paleo, and Phil Wadler for their collaboration, and to colleagues from the Universities of 
Kent and Leicester for their comments on previous presentations of this work.
